Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-03 p2/axiom-proof.tex
All proofs for the rules

\begin{proof}
\end{proof}

>>>>

\begin{proof}
If neither of the commands is an assertion command, then the claim follows from
\cref{simple_distant_pairs} in the following way.
We use an inverse proof and assume that $\cxypnv\cc\czwnv$ is not a construction pair,
none of the commands is an assertion command, and $\wrksx{\cxypnv\cc\czwnv}$.
Therefore \cref{simple_distant_pairs} applies to this sequence, and the two commands
must form a construction or destruction pair. This is a contradiction as due to
the relationship between the nodes, they cannot form a destruction pair, and
they do not form a construction pair by assumption.

Otherwise, let $\FS_1$ be $\cxypnv\aFS$, and $\FS_2$ be $(\cxypnv\cc\czwnv)\aFS$.
If $\cxypnv=\cbba{\pn}$ (the only assertion command it can be given the conditions),
then either $\FS_1$ is broken, or
$\FS(\pn)=\FS_1(\pn)=\FS_2(\pn)=\empt$.
Since $\czwnv\neq\cbba{n}$, we know that either $\czwnv$ breaks $\FS_1$,
or, depending on $z$ and $w$, either $\FS_1(n)\neq\empt$ or $\FS_2(n)\neq\empt$.
In any case $\FS_2$ will be broken at $\pn$ which is empty but at one point has a non-empty child.

Finally, if $\czwnv=\cdda{n}$, we can proceed in a similar way,
as since $\cxypnv\neq\cdda{n}$, we know at one point the value at $\pn$ is not a directory.
\end{proof}

\cref{ax_directparent_breaks}

\begin{proof}
This proof follows the same logic as that of \cref{ax_directchild_breaks},
using destruction pairs instead of construction pairs.
\end{proof}

\cref{ax_distantrel_breaks}

\begin{proof}
Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions,
and there is an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
If $\czwnv\neq\cbba{n}$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,
and therefore $\FS(\parentf{n})$ must be a directory for the filesystem to satisfy
the tree property at all times.
However, from $\cxynnv\neq\cdda{\nn}$ we also know that either $\FS(\nn)$ 
(before applying $\cxynv$) or $\cxynv\aFS(\nn)$ (after applying $\cxynv$)
is not a directory. Depending on which is true, we have a point in the sequence
of applying the commands where the filesystem cannot satify the tree property
and therefore becomes broken as $\parentf{n}$, a descendant of $\nn$, contains
a directory and so must all its ancestors.
\end{proof}

\cref{ax_child_assert}

\begin{proof}
Since $\cxynnv\neq\cdda{\nn}$, we know that
either $\cxynnv\aFS$ is broken, or, depending on $x$ and $y$,
either $\FS(\nn)\neq\vald$, or $\cxynnv\aFS(\nn)\neq\vald$.
In the latter two cases $\FS$ must be empty at all descendants of $\nn$
for it to satisfy the tree property.
The assertion command $\cbba{n}$ will therefore not break $\FS$.
\end{proof}

\cref{ax_parent_assert}

\begin{proof}
This proof follows the same logic as that of \cref{ax_child_assert}.
\end{proof}

\cref{ax_assert}

\begin{proof}
As for an assertion command $\cxynv$, $x=y$, we see that it either
breaks a filesystem, or leaves it in the same state.
\end{proof}

### 2018-07-03 p2/axioms.tex
All proofs for the rules

\item\mlabel{ax_directchild_breaks}
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxynnv\cc\czwnv \equiv \cbrk$ where $\cxy\neq\cdd$ and $\czw\neq\cbb$.

\item\mlabel{ax_directparent_breaks}
Commands on a child and parent node break every filesystem
if the pair is not a destruction pair
and the commands do not simply assert an empty node at the child
or a directory at the parent:
$\cxynv\cc\czwnnv \equiv \cbrk$ where $\cxy\neq\cbb$ and $\czw\neq\cdd$.

@@

\item\mlabel{ax_child_assert}
An assertion command can be freely added on a descendant node
next to a command that does not simply assert a directory:
\[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
where $\nn\descendant n$ and $\cxy\neq\cdd$.

\item\mlabel{ax_parent_assert}
An assertion command can be freely added on an ancestor node
next to a command that does not simply assert an empty node:
\[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
where $\nn\descendant n$ and $\cxy\neq\cbb$.

@@

These claims are easy but tedious to check.
To ensure that all cases were considered when verifying these claims,
a computer program was prepared that models the relevant parts of
a filesystem and checks the results of applying all different command pairs
against the above claims.\footnote{The program is accessible at \\ 
https://github.com/csirmaz/AlgebraicSyncPaper/blob/master/p2/prove.py.}

For \cref{ax_distantrel_breaks}, we also provide a simple proof.
Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions in the \namecref{ax_distantrel_breaks},
and there is an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
If $\czw\neq\cbb$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,
and therefore $\FS(\parentf{n})$ must be a directory for the filesystem to satisfy
the tree property at all times.
However, from $\cxy\neq\cdd$ we also know that either $\FS(\nn)$ 
(before applying $\cxynv$) or $\cxynv\aFS(\nn)$ (after applying $\cxynv$)
is not a directory. Depending on which is true, we have a point in the sequence
of applying the commands where the filesystem cannot satify the tree property
and therefore becomes broken as $\parentf{n}$, a descendant of $\nn$, contains
a directory and so must all its ancestors.

For \cref{ax_child_assert,ax_parent_assert}, we note that these claims
easily follow from the fact that the commands are adjacent to each other.

Finally, we have included \cref{ax_directchild_breaks,ax_directparent_breaks}
for completeness, but we will use the more generic \cref{simple_distant_pairs},
which extends these rules to non-adjacent commands, although only in the case
of command sequences without any assertion commands.

>>>>

\item\mlabel{ax_directchild_breaks}
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxypnv\cc\czwnv \equiv \cbrk$ where $\cxypnv\cc\czwnv$ is not a construction pair, 
$\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.

\item\mlabel{ax_directparent_breaks}
Commands on a child and parent node break every filesystem
if the pair is not a destruction pair
and the commands do not simply assert an empty node at the child
or a directory at the parent:
$\cxynv\cc\czwpnv \equiv \cbrk$ where $\cxynv\cc\czwpnv$ is not a destruction pair,
$\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.

@@

\item\mlabel{ax_child_assert}
An assertion command can be freely added on a descendant node
next to a command that does not simply assert a directory:
\[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
where $\nn\descendant n$ and $\cxynnv\neq\cdda{\nn}$.

\item\mlabel{ax_parent_assert}
An assertion command can be freely added on an ancestor node
next to a command that does not simply assert an empty node:
\[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
where $\nn\descendant n$ and $\cxynv\neq\cbba{n}$.

@@

We have included \cref{ax_directchild_breaks,ax_directparent_breaks}
for completeness, but we will use the more generic \cref{simple_distant_pairs},
which extends these rules to non-adjacent commands, although only in the case
of command sequences without any assertion commands.
